Tables and Figures - Supplement A, B and C

### 2019-12-20 code/06_Supplement-tables-figures.Rmd
Updated Figure S1A with a Fisher's z panel

This document contains the tables and figures from Supplement A, B and C for the project "Heterogeneity in direct replications in psychology and its association with effect size".

@@

#Add rp and k to the data-frame
het <- dat %>%
  filter(effect %in% res2$effect) %>% 
  select(rp, Site, effect, effect_type) %>%
  group_by(rp, effect) %>%
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>%
  left_join(res2) %>%
  mutate(effect_type = recode(effect_type,
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>%
  ungroup()

d <- het %>% filter(effect_type == "SMD.") %>%
  mutate(sigma2 = tau2/(I2/100) - tau2) #add 'typical within study variance' per project

@@

```{r tau-vs-tau}
b <- select(a, effect, tau2) %>%
  left_join(select(d, effect, tau2), by = "effect") #add point-biserial transformation tau2 to untransformed
```

```{r b-plot-1}
b_plot <- ggplot(b, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) +
  geom_point() +
  ggtitle("SMD vs. Point biserial") +
  scale_x_continuous(name = "Tau (SMD)") +
  scale_y_continuous(name = "Tau (Point-biserial r)")

@@

@@

cowplot::plot_grid(a_plot, b_plot, ncol = 1, labels = "AUTO")

@@

_Figure S1A_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into point-biserial correlations for all effects reported as SMDs in Many Labs 1. Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text). Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations.

@@

#Examine effects of larger effect size on transformation
transform_d_to_r(c(0, 0.1, 1, 1.1, 2, 2.1), n1 = 100, n2 = 100) #sourced function

#to find out which point is which effect in Panel c. 
c_plot + ggrepel::geom_label_repel(data = d, aes(label = effect))

@@

**Note.** Column headers indicate the degree of simulated heterogeneity where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75%) respectively. Medium effect size is as defined by Cohen (1988). Code to reproduce table: https://osf.io/j9zyd/?view_only=e6639d8d4f924739a7310782fbbb4e06

>>>>

This document contains the tables and figures from Supplement A, B and C for the project "Heterogeneity in direct replications in psychology and its association with effect size". This file can be found at: osf.io/bm2wa/?view_only=e6639d8d4f924739a7310782fbbb4e06

@@

b <- select(a, effect, tau2) %>%
  left_join(select(res2, effect, tau2), by = "effect") #add point-biserial transformation tau2 to untransformed

@@

```{r b-plot}
b_plot <- ggplot(b, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) +
  geom_point() +
  ggtitle("SMD vs. Point biserial") +
  scale_x_continuous(name = "Tau (SMD)") +
  scale_y_continuous(name = "Tau (Point-biserial r)")

@@

```{r fisher-transformed}
res3 <- dat %>%
  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "d") %>%
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map(transform_MA, fisher = TRUE) %>% #Fisher-transformed
  map_dfr(summarizer, .id = "effect")

d <- select(a, effect, tau2) %>%
  left_join(select(res3, effect, tau2), by = "effect") #add fisher-transformed point-biserial transformation tau2 to untransformed
```

```{r c-plot}
c_plot <- ggplot(d, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) +
  geom_point() +
  ggtitle(expression(bold(paste("SMD vs. Fisher's ", italic(z))))) +
  scale_x_continuous(name = "Tau (SMD)") +
  scale_y_continuous(name = expression(paste("Tau (Fisher's ", italic(z), ")")))
```

@@

cowplot::plot_grid(a_plot, b_plot, c_plot, ncol = 1, labels = "AUTO")

@@

_Figure S1A_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into point-biserial correlations for all effects reported as SMDs in Many Labs 1. Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text). Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations. Panel C shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations and subsequently to Fisher's _z_.

@@

#Examine effects of larger effect size on transformation to point-biserial
transform_d_to_r(c(0, 0.1, 1, 1.1, 2, 2.1), n1 = 100, n2 = 100) #sourced function

#to find out which point is which effect in Panel C. 
c_plot + ggrepel::geom_label_repel(data = d, aes(label = effect))

#Examine effects of larger effect size on transformation to Fisher's z
transform_d_to_r(c(0, 0.1, 1, 1.1, 2, 2.1), n1 = 100, n2 = 100, fisher = TRUE) #sourced function

@@

**Note.** Column headers indicate the degree of simulated heterogeneity where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75%) respectively. Medium effect size is as defined by Cohen (1988).
